Exploring Determinants of Child Mortality Globally (2022): The Role of Vaccination, Healthcare Spending, and Nutrition

### 2024-11-28 paper/paper.qmd
styler change

library(tidyverse)

```

@@

# Read the data
data <- read.csv(file = (here::here('data/01-raw_data/raw_data_Mortality.csv')))

@@

analysis_data <- read_parquet(file = (here::here('data/02-analysis_data/analysis_data.parquet')))

# Create the histogram
ggplot(analysis_data, aes(x = Mortality)) +
  geom_histogram(binwidth = 0.3, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Under-Five Mortality Rate",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )

```

@@

analysis_data <- read_parquet(file = (here::here('data/02-analysis_data/analysis_data.parquet')))

@@

raw_data <- read.csv(file = (here::here('data/01-raw_data/raw_data_Healthexpense.csv')))

analysis_data <- read_parquet(file = (here::here('data/02-analysis_data/analysis_data.parquet')))

@@

modelsummary(list("Mortality rate model" = model1), fmt = 4, statistic = c("({conf.low}, {conf.high})"))

```

>>>>

library(tidyverse)
```

@@

# Read the data
data <- read.csv(file = (here::here("data/01-raw_data/raw_data_Mortality.csv")))

@@

analysis_data <- read_parquet(file = (here::here("data/02-analysis_data/analysis_data.parquet")))

# Create the histogram
ggplot(analysis_data, aes(x = Mortality)) +
  geom_histogram(binwidth = 0.3, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Under-Five Mortality Rate",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )
```

@@

analysis_data <- read_parquet(file = (here::here("data/02-analysis_data/analysis_data.parquet")))

@@

raw_data <- read.csv(file = (here::here("data/01-raw_data/raw_data_Healthexpense.csv")))

analysis_data <- read_parquet(file = (here::here("data/02-analysis_data/analysis_data.parquet")))

@@

modelsummary(list("Mortality rate model" = model1), fmt = 4, statistic = c("({conf.low}, {conf.high})"))
```
